%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta, 
    urlcolor=blue,
}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Konstantin Amelichev} % Your name
\address{(+7)9671295255 \\ kostya.amelichev@gmail.com} % Your phone number and email
\address{\href{http://github.com/kik0s}{github: KiK0S} \\ \href{http://codeforces.com/profile/kikos}{codeforces: KiKoS}}

\begin{document}

\begin{rSection}{Education}

{\bf Higher School of Economics, Moscow} \hfill {\em September 2019 - June 2023} \\ 
Bachelor in Applied Mathematics and Information Science.

\end{rSection}

\begin{rSection}{Work Experience}

{\bf Tinkoff.ru, Moscow} \hfill {\em September 2020 - December 2020} \\ Backend internship; working on ad services: processing user's information before showing relevant ads. \\ Used C++, Boost, rapidjson. \\
{\bf Tinkoff Generation, Moscow} \hfill {\em September 2019 - Present} \\ Algorithms and data structures teacher for high school student's group. \\ Used, C++, Python, Polygon, testlib.
\end{rSection}

\begin{rSection}{Courses}
{\bf \href{http://github.com/kik0s/tink}{\underline{Tinkoff Generation}}} \hfill {\em September 2018 - June 2019} \\
Took courses of algorithms, data structures, machine learning, deep learning, math. \\
{\bf \href{http://github.com/it-church/rbtrf-2018}{\underline{Robotics}}} \hfill {\em September 2015 - March 2020} \\
Took robotics courses in my high school, where worked with Arduino and other microcontrollers. \\
\end{rSection}



\begin{rSection}{Projects}
{\bf \href{http://github.com/kik0s/3d-framework}{\underline {3d-framework}}} \hfill {\em Summer 2020} \\
Aim of the project is to make a framework for displaying 3-dimensional world, supporting any world transformations.
Used C++, sfml-graphics. \\
{\bf \href{http://github.com/kik0s/codememes}{\underline {Codenames AI}}} \hfill {\em Summer 2019}\\
Aim of the project was to make Telegram bot providing interface to play Codenames and AI as an opponent or a teammate. Used Python, gensim Word2Vec, python-telegram-bot.\\
{\bf \href{http://github.com/kik0s/spox}{\underline {Logs visualiser}}} \hfill {\em Spring 2019} \\
Aim of the project was to make a demo of desktop client which can visualise some information taken from sensors. Used Java, Swing.\\
{\bf \href{http://github.com/kik0s/dfvp}{\underline{Client-server game}}} \hfill {\em Summer 2018}\\
Aim of the project was to create a simple desktop client-server game. Used Python, pygame. \\
{\bf \href{http://github.com/it-church/neworgshop}{\underline{Map of Moscow organic shops}}} \hfill {\em Spring 2018}\\
Aim of the project was to create an Android application to provide users organic shops on a map and some information about them. Used Java, Yandex map API.
\end{rSection}


\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming languages \ & Python, C++, Java \\
Frameworks \ & Pandas, Numpy, Sklearn, Pytorch, Boost, python-telegram-bot\\
Tools \ & Git, Linux, Latex, SQL, Docker, CMake, MongoDB \\
Languages \ & Russian (native), English (free in use)
\end{tabular}

\end{rSection}

\begin{rSection}{Achievements \& Awards} 
    Gold medal of Russian national olympiad in informatics, 2019

    \item Silver medal of Russian national olympiad in informatics, 2018
    
    \item Candidate for master of sport in orienteering
\end{rSection}

\end{document}
